\vspace{-1em}Formulating RDF Constraints Generically and Validating RDF Data Out-Of-The-Box

### 2015-05-25 paper/paper 2/dc-2015.tex
RDF Constraints Vocabulary

% Anpassungen an DC Template
\usepackage[a4paper, left=2.9cm,right=2.87cm,bottom=3cm,top=3cm,headsep=1.27cm]{geometry}
\setlength{\parskip}{0.5em}
\renewcommand{\tablename}{TABLE} 
\renewcommand{\figurename}{FIG} 
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 2pt minus 2pt}{6pt plus 1pt minus 1pt}
\titlespacing\subsection{0pt}{12pt plus 2pt minus 2pt}{3pt plus 1pt minus 1pt}
\addtokomafont{title}{\fontsize{14pt}{1em}\selectfont}
\setkomafont{section}{\fontsize{12pt}{0pt}\selectfont}
\addtokomafont{subsection}{\fontsize{11pt}{0pt}\selectfont}
\addtokomafont{author}{\fontsize{12pt}{1em}\selectfont}
\usepackage{scrpage2}
\clearscrheadfoot
\pagestyle{scrheadings}
\renewcommand*{\titlepagestyle}{scrheadings}
\chead{\fontsize{11pt}{0pt}\selectfont Proc. Int'l Conf. on Dublin Core and Metadata Applications 2015}
\usepackage{apacite}

@@

@@

We evaluated for the five most common constraint languages which constraint types they enable to express \cite{BoschNolleAcarEckert2015}.
As there exists no single best solution and none of the languages is able to meet all requirements raised by data practitioners,
%which can be used to express constraints and to validate RDF data, 
%(e.g. existential and universal quantification, cardinality restrictions, and exclusive or of properties)
%\section{Ideas}
%constraint design patterns:
% - ontology design pattern.org
% - DSP uses other design pattern
% - constraint elements are the same / 
% - constraint / constraint elements / constraint design patterns / constraint language
%dependency between requirements / when this requirements is fulfilled then this is also fulfilled (e.g. min card and requ. car)
%min car more powerful than req. propery
the idea behind this paper is to satisfy all RDF validation requirements
by representing constraints of any constraint type in a generic way using a lightweight vocabulary which consists of only a few terms (Section \ref{sec:vocabulary}).
The constraint type \emph{minimum qualified cardinality restrictions} (\emph{R-75}) can be instantiated to ensure
that \emph{publications} must have at least one \emph{author} which must be a \emph{person}.
This constraint can either be represented generically by \emph{description logics (DL)} {\small\ms{(Publication $\sqsubseteq$ $\geq$1 author.Person)}} or specifically by multiple domain-specific constraint languages:

@@

As every \emph{publication} must have at least one \emph{author} which must be a \emph{person}, 
and since the book \emph{The-Lord-Of-The-Rings} is a \emph{publication} {\small\ms{(rdf:type(The-Lord-Of-The-Rings, Publication)),}} 
it must have at least one \emph{author} relationship to a \emph{person}.
Constraint violations are raised either (1) if
\emph{The-Lord-Of-The-Rings} does not have any \emph{author} relationship, or (2) if 
it has an \emph{author} which is not a \emph{person} \\
{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Hobbit)),}} 
or (3) if it has an \emph{author} for which no class is assigned
{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)).}}
In contrast, \emph{The-Lord-Of-The-Rings} is a valid \emph{publication}, if it is connected to a \emph{person} via the property \emph{author}
{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Person)).}}

As there is no standard way to formulate constraints, 
semantically equivalent \emph{cardinality restrictions} may be represented by multiple constraint languages that have different syntax and semantics.
This causes confusion and weakens the common understanding between several parties about the semantics of particular constraints. Also, it raises  questions on how to ensure high data quality. 
Therefore, when choosing a constraint language, say \ms{$\alpha$}, to express a constraint of an arbitrary constraint type, it should be possible to transform this constraint into a semantically equivalent constraint expressed by another constraint language \ms{$\beta$} (see Section \ref{sec:transformations}). 
This is important in order to enhance the interoperability of constraint languages and to resolve misunderstandings and ambiguities in the communication of RDF data producers and consumers, 
since constraint transformations avoid the necessity to understand several constraint languages.

We provide a validation environment\footnote{Online available at \url{http://purl.org/net/rdfval-demo}} which enables to validate RDF data according to constraints expressed by diverse  constraint languages.
As a second step, the \emph{RDF Validator} is extended by validating RDF data conforming to constraints of any constraint type represented by any constraint language,  
to perform validation on semantically equivalent \emph{specific constraints}, expressed by different constraint languages, 
i.e., validation is independent from the used constraint language (see Section \ref{sec:validation}). 
%i.e., validation leads to identical validation results - independently from the used constraint language (see section \ref{sec:validation}).
We are able to offer an already implemented validation mechanism for any \emph{specific constraint} out-of-the-box, 
(1) if we implement the validation of the corresponding \emph{generic constraint type} once and 
(2) if we transform semantically equivalent \emph{specific constraints} into generically expressed constraints.

@@

%This paper aims to address two main \textbf{audiences}:
%(1) RDF data providers and consumers seeking how to ensure high data quality and thus for ways to enhance the interoperability and common understanding of constraints expressible by multiple constraint languages and  
%(2) RDF practitioners thinking of how to provide aligned implementations for the validation of both existing an newly developed constraint languages.
The main contributions of this paper are:
(1) we provide a basic terminology and classification system for RDF constraints (Section \ref{sec:vocabulary}),
(2) we developed a vocabulary to describe constraints of any RDF constraint type generically and specified its underlying semantics (Section \ref{sec:vocabulary}),
(3) we show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and discuss why these transformations are useful (Section \ref{sec:transformations}), and
(4) we explain how to overcome the necessity to implement the validation of each constraint type for multiple constraint languages (Section \ref{sec:validation}).
%(if the validation is implemented once for the corresponding \emph{generic constraint type} to which the \emph{specific constraint type} is mapped)

@@

In order to develop a vocabulary to describe constraints of any constraint type in a generic way, what we need to do is to specify the vocabulary's underlying semantics and to define the basic terminology for the formulation of constraints.

\subsection{Underlying Semantics}

%The underlying \emph{semantics} for RDF validation is \emph{UNA} and \emph{CWA}.
RDF validation requires that different names represent different objects (\emph{unique name assumption (UNA)}), whereas,
\emph{OWL 2} is based on the {\em non-unique name assumption (nUNA)}.  
A data property is \emph{functional} (\emph{R-65}) if for each individual \emph{x}, there can be at most one distinct literal \emph{y} such that \emph{x} is connected by the data property to \emph{y}. 
When assuming \emph{UNA}, the functional property {\em title} {\small\ms{(funct (title))}} causes a clash
in case the book {\em Huckleberry-Finn} has more than one \emph{title}.
%(\ms{title(Huckleberry-Finn,} \ms{The-Adventures-of-Huckleberry-Finn)}, \ms{title} \ms{(Huckleberry-Finn,} \ms{Die-Abenteuer-des-Huckleberry-Finn)}).
Assuming \emph{nUNA}, however, reasoning concludes that the titles {\em The-Adventures-of-Huckleberry-Finn} and {\em Die-Abenteuer-des-Huckleberry-Finn} are the same. 
%(\ms{\{The-Adventures-of-Huckleberry-Finn\}} = \ms{\{Die-Abenteuer-des-Huckle} \ms{berry-}\ms{Finn\}}).

Reasoning in \emph{OWL 2} is based on the {\em open-world assumption (OWA)}, i.e., a statement cannot be inferred to be false if it cannot be proved to be true. 
%which fits its primary design purpose to represent knowledge on the World Wide Web. 
%Most of the constraint languages except OWL, have a major shortcoming of redundancy.
%With its open-world semantics, used as a constraint language, OWL solves the redundancy problem. 
%\tb{the following example does not show the redundancy problem!}
%\tb{2. benefit: reasoning solves redundancy problem}
As each \emph{book} must have a \emph{title} {\small\ms{(Book $\sqsubseteq \exists$ title.$\top$)}} and {\em Hamlet} is a \emph{book} {\small\ms{(Book(Hamlet)),}}
{\em Hamlet} must have at least one \emph{title}.
In an \emph{OWA} setting, this axiom does not cause a constraint violation (even if there is no explicitly defined \emph{title}), since there must be a \emph{title} for this \emph{book} which we may not know. 
On the other hand, RDF validation scenarios require the \emph{closed-world assumption (CWA)}, i.e., a statement is inferred to be false if it cannot be proved to be true.
When assuming the \emph{CWA}, a constraint violation is raised as there is no explicitly defined title. 
A constraint that says that a book must have at least one title in \emph{OWA}, 
does not mean that the title has to be unique. 
In every model  (an interpretation that makes a set of \emph{DL knowledge base} true), 
it can be the case that a book has a single title, however, 
this title is not unique. 
In some models it is \emph{The-Adventures-of-Huckleberry-Finn}, in others it is \emph{Die-Abenteuer-des-Huckleberry-Finn}. 
And since in every model there is only one, \emph{DL} sentences are satisfied. 
But this does not correspond to the intended constraint which is usual in \emph{CWA} way.   
%Classical constraint languages are based on the \emph{CWA} where constraints need to be satisfied only by named individuals which yields a constraint violation.
This ambiguity in semantics is one of the main reasons why \emph{OWL 2} has not been adopted as a standard constraint language for RDF validation in the past. 
In case we want to use \emph{OWL 2} as a constraint language, we adopt the same semantics (\emph{CWA} and \emph{UNA}) as for RDF validation in general. 
%In case we want to use \emph{OWL 2} as a constraint language, we adopt the same semantics (CWA) that is for RDF validation in general. 
%\tb{feedback from Erman: the major problem is semantics. OWL basically work in different semantics than others. And their semantics are formal. Closed world vs. Open World is also a part of this. / Thomas: I think your issue is tackled now? No.}

@@

We recently published a technical report \cite{BoschNolleAcarEckert2015} (serving as appendix of this paper) in which
we describe the intended behavior of each constraint type in terms of validation results depending on \emph{CWA} and \emph{UNA}.
If any two constraints are semantically the same (w.r.t. RDF semantics), they should detect the same set of violations regardless of RDF data, 
which means whenever the constraints are applied to any RDF data they point out the same violations.
To be able to define mappings between semantically equivalent \emph{specific constraints} (expressed by different languages) and 
between \emph{specific constraints} and \emph{generic constraints},
we show for each constraint type that their constraints lead to exactly the same violations which shows that they behave in the same way. 
We express constraint types by different languages
to document identical semantics for these languages with regard to appropriate constraint types.

@@

\subsection{Basic Terminology}
%\subsection{Basic Terminology for the Formulation of RDF Constraints}

A \emph{constraint language} is a language which is used to formulate constraints.
The W3C Data Shapes working group defines \emph{RDF constraint} as a component of a schema what needs to be satisfied\footnote{\url{https://www.w3.org/2014/data-shapes/wiki/Glossary}}.
We identified four dimensions to classify constraint types:
\begin{itemize}
  \item \emph{Universality:} \emph{specific constraints} vs. \emph{generic constraints}
	\item \emph{Complexity:} \emph{simple constraints} vs. \emph{complex constraints}
	\item \emph{Context:} \emph{property constraints} vs. \emph{class constraints}
	\item \emph{DL Expressivity:} \emph{constraints expressible in DL} vs. \emph{constraints not expressible in DL}
\end{itemize}

As there are already five promising constraint languages and our purpose is not to put a new constraint language, we rather developed a very simple lightweight vocabulary (only three classes, three object properties, and three data properties) which is universal enough to describe constraints of any constraint type expressible by any constraint language (see the conceptual model in figure \ref{fig:RDF-CV-conceptual-model}).
We call this vocabulary the \emph{RDF Constraints Vocabulary (RDF-CV)}\footnote{Online available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}}.

\begin{figure}
	\centering
		\includegraphics[width=0.80\textwidth]{images/RDF-CV-conceptual-model.png}
	\caption{\emph{RDF Constraints Vocabulary (RDF-CV)} - conceptual model}
	\label{fig:RDF-CV-conceptual-model}
\end{figure}

Constraints can be expressed either generically (\emph{generic constraints}) by the \emph{RDF-CV}   
or specifically (\emph{specific constraints}) by domain-specific constraint languages.
As the \emph{RDF-CV} describes constraints generically, the vocabulary does not distinguish constraints according to the dimension \emph{universality}. 
The majority of the constraint types can be expressed in \emph{DL}.
In contrast, there are certain constraint types which cannot be expressed in \emph{DL}, but are also expressible by the \emph{RDF-CV} . 
\emph{Complex constraints} encompass \emph{simple constraints} (atomic constraints) and/or further \emph{complex constraints},
i.e. \emph{DL} statements representing \emph{complex constraints} are created out of \emph{DL} statements standing for atomic and composed constraints (if expressible in \emph{DL}). 
Simple constraints may be applied to either properties (\emph{property constraints}) or classes (\emph{class constraints}).
The \emph{RDF-CV} does not contain any terms standing for \emph{simple} and \emph{complex constraints}, since \emph{context classes} of \emph{simple constraints} are just reused within \emph{complex constraints} (\emph{simple constraints} associated with \emph{context classes} must hold for individuals of these \emph{context classes}). 
%\tb{Erman: If you say its expressible in RDF-CV, than you impose that RDF-CV is a language rather than a vocabulary. "in different contexts they call it signature which is the same thing". Generally, a language uses vocabulary to construct sentences, and the set of those sentences, is the language.} (see section \ref{sec:evaluation})
As a consequence, the distinction of \emph{property} and \emph{class constraints} is sufficient to describe constraints of all possible constraint types.
\tb{use RDF-CV / not: expressible in RDF-CV / RDF-CV is a vocabulary, not a language}

@@

\subsubsection{\emph{Simple Constraints} (Expressible in \emph{DL})}

Sub-classes of \emph{simple constraints} are \emph{property constraints} and \emph{class constraints} (see the \emph{RDF-CV} implementation model in figure \ref{fig:RDF-CV-implementation-model}). 
For both \emph{property} and \emph{class constraints} a \emph{context class}, a list of \emph{classes}, the \emph{constraining element}, and the \emph{constraining value} can be stated. 
Lists of \emph{left} and \emph{right properties} can only be specified for \emph{property constraints}.

\begin{figure}
	\centering
		\includegraphics[width=0.70\textwidth]{images/RDF-CV-implementation-model.png}
	\caption{\emph{RDF Constraints Vocabulary (RDF-CV)} - implementation model}
	\label{fig:RDF-CV-implementation-model}
\end{figure}

A \emph{simple constraint} holds for all individuals of a \emph{context class}.
Consider, e.g., the following \emph{minimum qualified cardinality restriction} on the object property \emph{author}, which restricts \emph{publications} to have at least one \emph{author} which is a \emph{person}: 
\begin{DL}
$Publication \sqsubseteq \geq1 author . Person $
\end{DL}
The cardinality restriction is a constraint on the property \emph{author} and is therefore classified as a \emph{property constraint} which holds for all individuals of the class \emph{Publication} (see Table \ref{tab:property-constraint-cardinality-restriction} for the mapping to \emph{RDF-CV}):

>>>>

% Anpassungen an DC Template
\usepackage[a4paper, left=2.9cm,right=2.87cm,bottom=3cm,top=3cm,headsep=1.27cm]{geometry}
\setlength{\parskip}{0.5em}
\renewcommand{\tablename}{TABLE} 
\renewcommand{\figurename}{FIG.} 
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 2pt minus 2pt}{6pt plus 1pt minus 1pt}
\titlespacing\subsection{0pt}{12pt plus 2pt minus 2pt}{3pt plus 1pt minus 1pt}
\addtokomafont{title}{\fontsize{14pt}{1em}\selectfont}
\setkomafont{section}{\fontsize{12pt}{0pt}\selectfont}
\addtokomafont{subsection}{\fontsize{11pt}{0pt}\selectfont}
\addtokomafont{author}{\fontsize{12pt}{1em}\selectfont}
\usepackage{scrpage2}
\clearscrheadfoot
\pagestyle{scrheadings}
\renewcommand*{\titlepagestyle}{scrheadings}
\chead{\fontsize{9pt}{0pt}\selectfont Proc. Int'l Conf. on Dublin Core and Metadata Applications 2015}
\usepackage{apacite}

@@

% just makes the table prettier (see \toprule, \bottomrule, etc. commands below)
\usepackage{booktabs}

\usepackage{tabularx}

\usepackage{float}

@@

We evaluated which constraint types the five most common constraint languages enable to express.
The evaluation is explained in detail in the appendix of this paper \cite{BoschNolleAcarEckert2015}.
Table \ref{tab:constraint-type-specific-expressivity} shows in percentage values (and absolute numbers in brackets) how many constraint types each language supports.

\begin{table}[H]
	\centering
	  %\caption{Constraint Type Specific Expressivity}
		\caption{Constraint Type Specific Expressivity of Constraint Languages}
	  \scriptsize
		\begin{tabular}{c|c|c|c|c}
      %\textbf{Expressivity Class} & $Expr(\overline{\mathcal{CT}_R})$ (42) & $Expr(\mathcal{CT}_R)$ (32) \\		
			\emph{DSP} & \emph{ReSh} & \emph{ShEx} & \emph{OWL 2} & \emph{SPIN} \\	
      \hline
			17.3 (14) & 25.9 (21) & 29.6 (24) & 67.9 (55) & \textbf{100.0} \textbf{(81)} 
		\end{tabular}
	\label{tab:constraint-type-specific-expressivity}
\end{table}

The fact that \emph{SPIN} supports all and that \emph{OWL 2} covers 2/3 of all constraint types
emphasizes the significant role \emph{SPIN} and \emph{OWL 2} play for the future development of constraint languages.
\emph{SPARQL} and therefore \emph{SPIN}, the \emph{SPARQL}-based way to formulate and check constraints, is generally seen as the method of choice to validate data according to certain constraints \cite{Fuerber2010}, 
although, it is not ideal for their formulation. 
In contrast, high-level constraint languages, which may be placed on top of \emph{SPARQL} and \emph{SPIN}, are comparatively easy to understand and constraints can be formulated more concisely.

There exists no single best solution considered as high-level intuitive constraint language which enables to express constraints easily and concisely and which is able to meet all requirements raised by data practitioners.
%which can be used to express constraints and to validate RDF data, 
%(e.g. existential and universal quantification, cardinality restrictions, and exclusive or of properties)
%\section{Ideas}
%constraint design patterns:
% - ontology design pattern.org
% - DSP uses other design pattern
% - constraint elements are the same / 
% - constraint / constraint elements / constraint design patterns / constraint language
%dependency between requirements / when this requirements is fulfilled then this is also fulfilled (e.g. min card and requ. car)
%min car more powerful than req. propery
Thus, the idea behind this paper is to satisfy all RDF validation requirements
by representing constraints of any constraint type in a generic way using a lightweight vocabulary which consists of only a few terms.
We lately published a technical report (serving as second appendix of this paper) in which we describe the vocabulary in detail \cite{BoschEckert2015-2} (Section \ref{sec:vocabulary}).
The constraint type \emph{minimum qualified cardinality restrictions} (\emph{R-75}) can be instantiated to ensure
that \emph{publications} must have at least one \emph{author} which must be a \emph{person}.
This constraint can either be represented generically by \emph{description logics (DL)} {\small\ms{(Publication $\sqsubseteq$ $\geq$1 author.Person)}} or specifically by multiple domain-specific constraint languages:

@@

As every \emph{publication} must have at least one \emph{author} which must be a \emph{person} 
and since the book \emph{The-Lord-Of-The-Rings} is a \emph{publication} {\small\ms{(rdf:type(The-Lord-Of-The-Rings, Publication)),}} 
the book must have at least one \emph{author} relationship to a \emph{person}.
The constraint is violated either (1) if
\emph{The-Lord-Of-The-Rings} does not have any \emph{author} relationship, 
or (2) if the book has an \emph{author} which is not a \emph{person}
{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)},} {\small\ms{rdf:type(Tolkien, Hobbit)),}} 
or (3) if the book has an \emph{author} whose class is unknown
{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)).}}
In contrast, the book is a valid \emph{publication}, if it is connected to a \emph{person} via the property \emph{author}
{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Person)).}}

As there is no standard way to formulate constraints, 
semantically equivalent \emph{minimum qualified cardinality restrictions} may be represented by multiple languages - each of them having different syntax and semantics.
This causes confusion,
weakens the common understanding between several parties about the meaning of particular constraints, and
raises the question on how to ensure high data quality. 
Therefore, when choosing a language, say \ms{$\alpha$}, to express a constraint of an arbitrary constraint type, 
it should be possible to transform the constraint into a semantically equivalent constraint expressed by another constraint language \ms{$\beta$} (see Section \ref{sec:transformations}). 
This is important in order to enhance the interoperability of constraint languages and to resolve misunderstandings and ambiguities in the communication of RDF data producers and consumers 
since automatically performed constraint transformations avoid the necessity to understand several languages.

We use \emph{SPIN} as basis to develop a validation environment\footnote{Online demo available at \url{http://purl.org/net/rdfval-demo}, source code available at: \url{https://github.com/boschthomas/rdf-validator}\label{rdf-validator}} to validate RDF data according to constraints of constraint types which are expressible by arbitrary constraint languages by mapping them to \emph{SPIN}\footnote{\emph{SPIN} mappings available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/SPIN}\label{spin-mappings}} \cite{BoschEckert2014-2}.
The next step, however, is to extend the \emph{RDF Validator} to validate RDF data conforming to constraints of each of the 81 constraint types.

Validation on semantically equivalent constraints, expressed by different constraint languages, 
should lead to identical validation results, 
i.e., validation should be performed independently from the used language (see Section \ref{sec:validation}).

We are able to offer already implemented validation for constraints of constraint types expressed by arbitrary languages out-of-the-box, 
(1) if we implement the validation of the corresponding generically represented constraint types once and 
(2) if we transform semantically equivalent specifically expressed constraints into generically expressed constraints.

@@

%This paper aims to address two main \textbf{audiences}:
%(1) RDF data providers and consumers seeking how to ensure high data quality and thus for ways to enhance the interoperability and common understanding of constraints expressible by multiple constraint languages and  
%(2) RDF practitioners thinking of how to provide aligned implementations for the validation of both existing an newly developed constraint languages.
The main contributions of this paper are:
(1) We provide a basic terminology and classification system for RDF constraints (Section \ref{sec:vocabulary}).
(2) We developed a vocabulary to describe constraints of any RDF constraint type generically (Section \ref{sec:vocabulary}).
(3) We show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and discuss why these transformations are useful (Section \ref{sec:transformations}).
(4) We explain how to overcome the necessity to implement the validation of each constraint type for multiple constraint languages (Section \ref{sec:validation}).
%(if the validation is implemented once for the corresponding \emph{generic constraint type} to which the \emph{specific constraint type} is mapped)

@@

Prerequisites to develop a vocabulary to describe constraints of any constraint type in a generic way are 
(1) to specify the underlying semantics for validation and thus for the vocabulary and (2) to define a basic terminology and classification system to formulate constraints.

\subsection{Semantics for RDF Validation}

RDF validation and \emph{OWL 2} assume different semantics. 
This ambiguity in semantics is one of the main reasons why \emph{OWL 2} has not been adopted as a standard constraint language for RDF validation in the past.
We compare semantics of RDF validation and of \emph{OWL 2} as we consider \emph{OWL 2} as a constraint language 
when RDF validation semantics are applied.
%
\emph{OWL 2} is based on the {\em open-world assumption} (\emph{OWA}), i.e., a statement cannot be inferred to be false if it cannot be proved to be true  which fits its primary design purpose to represent knowledge on the \emph{WWW}. 
As each \emph{book} must have a \emph{title} {\small\ms{(Book $\sqsubseteq \exists$ title.$\top$)}} and {\em Hamlet} is a \emph{book} {\small\ms{(Book(Hamlet)),}}
{\em Hamlet} must have at least one \emph{title} as well.
In an \emph{OWA} setting, this constraint does not cause a violation, even if there is no explicitly defined \emph{title}, since there must be a \emph{title} for this \emph{book} which we may not know ($\mathcal{K}$ is consistent).
As RDF validation has its origin in the XML world
many RDF validation scenarios require the {\em closed-world assumption} (\emph{CWA}), i.e., a statement is inferred to be false if it cannot be proved to be true.
Thus, classical constraint languages are based on the \emph{CWA} where constraints need to be satisfied only by named individuals. 
In the example, the \emph{CWA} yields to a violation since there is no explicitly defined \emph{title} for the \emph{book} {\em Hamlet}. 
%
Validation requires that different names represent different objects (\emph{unique name assumption (UNA)}), whereas,
\emph{OWL 2} is based on the {\em non-unique name assumption (nUNA)}.  
If we define the property \emph{title} to be functional {\small\ms{(funct (title)),}} a \emph{book} can have at most one distinct \emph{title}.
\emph{UNA} causes a clash
if the \emph{book} {\em Huckleberry-Finn} has more than one \emph{title}.
For \emph{nUNA}, however, reasoning concludes that the \emph{title} {\em The-Adventures-of-Huckleberry-Finn} must be the same as the \emph{title} {\em Die-Abenteuer-des-Huckleberry-Finn} 
which resolves the violation. 
%Although, \emph{OWL 2} does not assume \emph{UNA}, \emph{OWL 2} has the constructs \emph{owl:sameAs} and \emph{owl:differentFrom} to state that two names are the same or different.
If validation would assume \emph{OWA} and \emph{nUNA}, validation won’t be that restrictive and therefore we won’t get the intended validation results.

%\emph{OWL 2} reasoning is based on the {\em open-world assumption (OWA)}, i.e., a statement cannot be inferred to be false if it cannot be proved to be true. 
%%which fits its primary design purpose to represent knowledge on the World Wide Web. 
%%Most of the constraint languages except OWL, have a major shortcoming of redundancy.
%%With its open-world semantics, used as a constraint language, OWL solves the redundancy problem. 
%%\tb{the following example does not show the redundancy problem!}
%%\tb{2. benefit: reasoning solves redundancy problem}
%As each \emph{book} must have a \emph{title} {\small\ms{(Book $\sqsubseteq \exists$ title.$\top$)}} and {\em Hamlet} is a \emph{book} {\small\ms{(Book(Hamlet)),}}
%{\em Hamlet} must have at least one \emph{title}.
%In an \emph{OWA} setting, this axiom does not cause a constraint violation (even if there is no explicitly defined \emph{title}), since there must be a \emph{title} for this \emph{book} which we may not know. 
%On the other hand, RDF validation scenarios require the \emph{closed-world assumption (CWA)}, i.e., a statement is inferred to be false if it cannot be proved to be true.
%When assuming the \emph{CWA}, a constraint violation is raised as there is no explicitly defined title. 
%A constraint that says that a book must have at least one title in \emph{OWA}, 
%does not mean that the title has to be unique. 
%In every model  (an interpretation that makes a set of \emph{DL knowledge base} true), 
%it can be the case that a book has a single title, however, 
%this title is not unique. 
%In some models it is \emph{The-Adventures-of-Huckleberry-Finn}, in others it is \emph{Die-Abenteuer-des-Huckleberry-Finn}. 
%And since in every model there is only one, \emph{DL} sentences are satisfied. 
%But this does not correspond to the intended constraint which is usual in \emph{CWA} way.   
%%Classical constraint languages are based on the \emph{CWA} where constraints need to be satisfied only by named individuals which yields a constraint violation.
%This ambiguity in semantics is one of the main reasons why \emph{OWL 2} has not been adopted as a standard constraint language for RDF validation in the past. 
%In case we want to use \emph{OWL 2} as a constraint language, we adopt the same semantics (\emph{CWA} and \emph{UNA}) as for RDF validation in general. 
%In case we want to use \emph{OWL 2} as a constraint language, we adopt the same semantics (CWA) that is for RDF validation in general. 
%\tb{feedback from Erman: the major problem is semantics. OWL basically work in different semantics than others. And their semantics are formal. Closed world vs. Open World is also a part of this. / Thomas: I think your issue is tackled now? No.}

@@

Differences in semantics may lead to differences in validation results when applied to particular constraint types.
For the majority of the constraint types, validation results differ (1) if the \emph{CWA} or the \emph{OWA} and (2) if the \emph{UNA} or the \emph{nUNA} is assumed \cite{BoschNolleAcarEckert2015}.
If any two constraints are semantically the same (w.r.t. RDF semantics), they should detect the same set of violations regardless of RDF data, 
which means whenever the constraints are applied to any RDF data they point out the same violations.
To be able to define mappings between semantically equivalent \emph{specific constraints} (expressed by different languages) and 
between \emph{specific constraints} and \emph{generic constraints},
we show for each constraint type that their constraints lead to exactly the same violations which shows that they behave in the same way. 
We express constraint types by different languages
to document identical semantics for these languages with regard to appropriate constraint types.

@@

\subsection{Basic Terminology and Classification System for RDF Constraints}
%\subsection{Basic Terminology for the Formulation of RDF Constraints}

A \emph{constraint language} is a language which is used to formulate constraints.
The \emph{W3C} working group defines \emph{RDF constraint} as a component of a schema what needs to be satisfied\footnote{\url{https://www.w3.org/2014/data-shapes/wiki/Glossary}}.
As there are already five promising constraint languages, 
our purpose is not to propose a new language.
We rather developed a very simple lightweight vocabulary,
consisting of only three classes, three object properties, and three data properties, 
which is universal enough to describe constraints of any constraint type.
We call this vocabulary the \emph{RDF Constraints Vocabulary (RDF-CV)}\footnote{Online available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}} whose conceptual model is shown in Figure \ref{fig:RDF-CV-conceptual-model}.
\begin{figure}
	\centering
		\includegraphics[width=0.60\textwidth]{images/RDF-CV-conceptual-model.png}
	\caption{\emph{RDF Constraints Vocabulary (RDF-CV)} - Conceptual Model}
	\label{fig:RDF-CV-conceptual-model}
\end{figure}

We identified four dimensions to classify sets of constraints which can be instantiated from constraint types.
For each constraint type, we evaluated \cite{BoschNolleAcarEckert2015} in with which set of constraints their instances of contained.
For each set of constraints, we state the rounded number of associated constraint types in brackets.
%\begin{itemize}
  %\item \emph{Universality:} \emph{specific constraints} vs. \emph{generic constraints}
	%\item \emph{Complexity:} \emph{simple constraints} vs. \emph{complex constraints}
	%\item \emph{Context:} \emph{property constraints} vs. \emph{class constraints}
	%\item \emph{DL Expressivity:} \emph{constraints expressible in DL} vs. \emph{constraints not expressible in DL}
%\end{itemize}
%(1) \emph{Universality:} \emph{specific constraints} vs. \emph{generic constraints},
%(2) \emph{Complexity:} \emph{simple constraints} vs. \emph{complex constraints},
%(3) \emph{Context:} \emph{property constraints} vs. \emph{class constraints}, and
%(4) \emph{DL Expressivity:} \emph{constraints expressible in DL} vs. \emph{constraints not expressible in DL}.
\textbf{\emph{Universality}:}
Constraints are expressible either generically (\emph{generic constraints}) using the \emph{RDF-CV}   
or specifically (\emph{specific constraints}) by domain-specific constraint languages. 
\textbf{\emph{DL Expressivity}:}
The \emph{RDF-CV} allows to describe 
constraints which are \emph{expressible in DL} (70\%) and which are \emph{not expressible in DL} (30\%). 
In case a constraint type is \emph{expressible in DL}, we determined which \emph{DL} constructs are needed to express the constraint type.
In addition, we mapped constraints of each constraint type to \emph{generic constraints} conforming to the \emph{RDF-CV} \cite{BoschNolleAcarEckert2015}.
This way, we show that constraints of each constraint type are representable as \emph{generic constraints} and therefore can be described generically by means of the \emph{RDF-CV}.
\textbf{\emph{Complexity}:}
\emph{Simple constraints} (2/3) denotes the set of atomic constraints. 
%which can be instantiated from almost 2/3 of the constraint types.
\emph{Complex constraints} (1/4) is the set of constraints which are created out of \emph{simple} and/or other \emph{complex constraints}.
%and which are instances of 1/4 of the constraint types.
In case \emph{complex constraints} are expressible in \emph{DL}, 
\emph{DL} statements representing \emph{complex constraints} contain \emph{DL} statements standing for atomic and/or composed constraints. 
Nearly 15\% of the \emph{complex constraints}, however, can be formulated as \emph{simple constraints} when using them in terms of syntactic sugar. 
\textbf{\emph{Context}:}
\emph{Simple constraints} are applied on properties (\emph{property constraints}, 2/3),
on classes (\emph{class constraints}, 1/5), or
on properties and classes (\emph{property and class constraints}, 1/10).
%2/3 of all constraint types are types of \emph{property constraints}, 
%1/5 of \emph{class constraints}, and 
%approx. 10\% of \emph{property and class constraints}.
\emph{Simple constraints} must hold for individuals of their \emph{context classes}.
As \emph{context classes} of \emph{simple constraints} are reused within \emph{complex constraints},
it does not make sense to have terms standing for \emph{simple} and \emph{complex constraints} within the \emph{RDF-CV}. 
As a consequence, the distinction of \emph{property} and \emph{class constraints} is sufficient to generically describe constraints of all constraint types.
%\tb{use RDF-CV / not: expressible in RDF-CV / RDF-CV is a vocabulary, not a language}
Altogether, instances of the most of the constraint types are \emph{simple constraints on properties} which are \emph{expressible in DL}. 
%Thus, the majority of constraint types are directly and relatively easy formulated in form of \emph{simple constraints} which can be mapped to equivalent \emph{DL} constructs.

@@

The implementation model of the \emph{RDF-CV} (see Figure \ref{fig:RDF-CV-implementation-model}) shows that
both \emph{property constraints} and \emph{class constraints} are \emph{simple constraints}. 
%For both \emph{property} and \emph{class constraints} a \emph{context class}, a list of \emph{classes}, the \emph{constraining element}, and the \emph{constraining value} can be stated. 
%Lists of \emph{left} and \emph{right properties} can only be specified for \emph{property constraints}.
\begin{figure}
	\centering
		\includegraphics[width=0.60\textwidth]{images/RDF-CV-implementation-model.png}
	\caption{\emph{RDF Constraints Vocabulary (RDF-CV)} - Implementation Model}
	\label{fig:RDF-CV-implementation-model}
\end{figure}
A \emph{simple constraint} holds for all individuals of their \emph{context class}.
The \emph{minimum qualified cardinality restriction} {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person,}}
which restricts \emph{publications} to have at least one \emph{author} which must be a \emph{person},
is an example of a \emph{property constraint} on \emph{author}
which holds for all individuals of the class \emph{Publication}.
Table \ref{tab:property-constraint-cardinality-restriction} displays the mapping to the \emph{RDF-CV}:
\begin{table}[H]
  \scriptsize
  \sffamily
  \vspace{0cm}
	\caption{Property Constraint - Minimum Qualified Cardinality Restriction}
	\label{tab:property-constraint-cardinality-restriction}
	\centering
		\begin{tabular}{l|l|l|l|l|l|l}
      \textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      \hline
      property & Publication & author & - & Person & $\geq$ & 1 \\
		\end{tabular}
\end{table}
